sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-01-25 doc/paper-jss/owls.Rmd
Tweaks to reprex

```{r shapes, echo=FALSE}
if (!file.exists(here::here("data/ne_10m_lakes.rds"))) {
  zip_file <- paste0("https://www.naturalearthdata.com/http//www.naturalearthdata.com/",
    "download/10m/physical/ne_10m_lakes.zip")
  download.file(zip_file, destfile = here::here("data/ne_10m_lakes.zip"))
  unzip(here::here("data/ne_10m_lakes.zip"), exdir = here::here("data/ne_10m_lakes.rds"))
}
```

```{r shapes-read, echo=TRUE}
coast <- rnaturalearth::ne_coastline(scale = "medium", returnclass = "sf") %>%
  sf::st_transform(crs = Albers)
lakes <- sf::st_read(here::here("data/ne_10m_lakes.rds"), quiet = TRUE)
lakes <- lakes[lakes$scalerank == 0, ] %>% sf::st_transform(crs = Albers)
```

>>>>

```{r shapes, echo=FALSE}
if (!file.exists(here::here("data/ne_10m_lakes"))) {
  zip_file <- paste0("https://www.naturalearthdata.com/http//www.naturalearthdata.com/",
    "download/10m/physical/ne_10m_lakes.zip")
  download.file(zip_file, destfile = here::here("data/ne_10m_lakes.zip"))
  unzip(here::here("data/ne_10m_lakes.zip"), exdir = here::here("data/ne_10m_lakes"))
}
```

```{r shapes-read, echo=TRUE}
coast <- rnaturalearth::ne_coastline(scale = "medium", returnclass = "sf") %>%
  sf::st_transform(crs = Albers)
lakes <- sf::st_read(here::here("data/ne_10m_lakes"), quiet = TRUE)
lakes <- lakes[lakes$scalerank == 0, ] %>% sf::st_transform(crs = Albers)
```
